Revisiting `Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation

### 2023-06-14 analysis/R/04_rmd/01_dataGMTV.Rmd
improve reproducability

Having replicated Gaechter et al.'s main figures (more or less) the next step is to prepare the data we obtain in our experiment for the analysis. This will be done in the second report using simulated data.^[Eventually, one can use that report and apply it to the actual data.]

>>>>

Having replicated Gächter et al.'s main figures (more or less) the next step is to prepare the data we obtain in our experiment for the analysis. This will be done in the second report using my data.

### 2023-06-14 analysis/R/04_rmd/03_dataAnalyses.Rmd
improve reproducability

- We replicate a public goods experiment with dynamic interdependency and find similar results as @GACHTER2017.
- Absolute contributions increase over time.
- Just as in _static_ public goods experiments, the share of endowments contributed decreases over time.
- The richest groups earn fifteen times more than the poorest groups.
- While there clearly is growth, groups do not realize the maximal potential efficiency and earn just over `r main[treatment == "replication" & round == 10, mean(stock)/(80*1.5^10)*100] %>% round(digits=1)`% of what is possible.
- Even though we conducted the experiment online and remotely, dropouts (or "attrition") are no concern.
- Relying on an inexperienced non-convenience sample, `r trunc((R1[comprehension > 1] %>% NROW() / R1[!(is.na(comprehension))] %>% NROW())*100)`% of all participants stated that they understood the game.
- Participants make relatively fast decisions which makes longer games feasible in the future.^[Taken together with inefficient growth and the lack of dropouts, additional rounds are fairly cheap.]

@@

stargazer(lm(formula = stock ~ treatment, data = main_all),
          lm(formula = stock ~ treatment, data = main_poor),
          lm(formula = stock ~ treatment, data = main_rich),

@@

stargazer(lm(formula = gini ~ treatment, data = main_all),
          lm(formula = gini ~ treatment, data = main_poor),
          lm(formula = gini ~ treatment, data = main_rich),

@@

stargazer(lm(formula = pq01 ~ treatment, data = covs),
          lm(formula = pq02 ~ treatment, data = covs),
          lm(formula = pq03 ~ treatment, data = covs),
          lm(formula = pq04 ~ treatment, data = covs),
          lm(formula = pq05 ~ treatment, data = covs),

@@

stargazer(lm(formula = pq06 ~ treatment, data = covs),
          lm(formula = pq07 ~ treatment, data = covs),
          lm(formula = pq08 ~ treatment, data = covs),
          lm(formula = pq09 ~ treatment, data = covs),
          lm(formula = pq10 ~ treatment, data = covs),

@@

stargazer(lm(formula = pq11 ~ treatment, data = covs),
          lm(formula = pq12 ~ treatment, data = covs),
          lm(formula = pq13 ~ treatment, data = covs),
          lm(formula = pq14 ~ treatment, data = covs),

>>>>

- We replicate a public goods experiment with dynamic interdependency and find similar results as @GMTV2017.
- Absolute contributions increase over time.
- Just as in _static_ public goods experiments, the share of endowments contributed decreases over time.
- The richest groups earn fifteen times more than the poorest groups.
- While there clearly is growth, groups do not realize the maximal potential efficiency and earn just over `r main[treatment == "replication" & round == 10, mean(stock)/(80*1.5^10)*100] %>% round(digits=1)`% of what is possible.
- Even though we conducted the experiment online and remotely, dropouts (or "attrition") are no concern.
- Relying on an inexperienced non-convenience sample, `r trunc((R1[comprehension > 1] %>% NROW() / R1[!(is.na(comprehension))] %>% NROW())*100)`% of all participants stated that they understood the game.
- Participants make relatively fast decisions which makes longer games feasible in the future.^[Taken together with inefficient growth and the lack of dropouts, additional rounds are fairly cheap.]

@@

m1 <- lm(formula = stock ~ treatment, data = main_all)
m2 <- lm(formula = stock ~ treatment, data = main_poor)
m3 <- lm(formula = stock ~ treatment, data = main_rich)

stargazer(m1,
          m2,
          m3,

@@

m1 <- lm(formula = gini ~ treatment, data = main_all)
m2 <- lm(formula = gini ~ treatment, data = main_poor)
m3 <- lm(formula = gini ~ treatment, data = main_rich)

stargazer(m1,
          m2,
          m3,

@@

m5 <- lm(formula = pq01 ~ treatment, data = covs)
m6 <- lm(formula = pq02 ~ treatment, data = covs)
m7 <- lm(formula = pq03 ~ treatment, data = covs)
m8 <- lm(formula = pq04 ~ treatment, data = covs)
m9 <- lm(formula = pq05 ~ treatment, data = covs)

stargazer(m5,
          m6,
          m7,
          m8,
          m9,

@@

m10 <- lm(formula = pq06 ~ treatment, data = covs)
m11 <- lm(formula = pq07 ~ treatment, data = covs)
m12 <- lm(formula = pq08 ~ treatment, data = covs)
m13 <- lm(formula = pq09 ~ treatment, data = covs)
m14 <- lm(formula = pq10 ~ treatment, data = covs)

stargazer(m10,
          m11,
          m12,
          m13,
          m14,

@@

m15 <- lm(formula = pq11 ~ treatment, data = covs)
m16 <- lm(formula = pq12 ~ treatment, data = covs)
m17 <- lm(formula = pq13 ~ treatment, data = covs)
m18 <- lm(formula = pq14 ~ treatment, data = covs)
stargazer(m15,
          m16,
          m17,
          m18,

### 2023-06-14 analysis/article/paper.qmd
improve reproducability

pacman::p_load(magrittr, data.table, stringr, lubridate, glue, DescTools, haven, censReg,
               stargazer, vtable, ggplot2, patchwork, MetBrewer, Rmisc, knitr)
```

@@

# color
colors <- met.brewer(name="Tam",n=7,type="discrete")
colors <- c("#F3B05C", "#1E4A75", "#65B5C0", "#AD5E21")
# cPrimary = "#ffd353"
# cSecondary = "#9f2d55"
# cInfo = "#34168"
cPrimary = "#F3B05C"
cSecondary = "#1E4A75"
cInfo = "#36BFA2"
```

@@

```{r saveGMTV}
fileName <- "GMTV2017"
# save data
save(GMTV, file = paste0("../../data/processed/rda/", fileName, ".rda"))
write.csv(GMTV, file = paste0("../../data/processed/rda/", fileName, ".csv"))
```

>>>>

pacman::p_load(magrittr, data.table, stringr, lubridate, glue, haven, DescTools, censReg, stargazer, vtable, ggplot2, patchwork, Rmisc, knitr, rang)
```

```{r system_requirements}
#| eval: false
packages <- pacman::p_loaded()

graph <- rang::resolve(pkgs = packages,
                       snapshot_date = '2023-06-14')

export_rang(graph, '../requirements/article.R')
save(graph, file = '../requirements/article.rda')
```

@@

# color
cPrimary = "#F3B05C"
cSecondary = "#1E4A75"
cInfo = "#36BFA2"
```

@@

```{r saveGMTV}
fileName <- "GMTV2017"
# save data
save(GMTV, file = paste0("../../data/processed/rda/", fileName, ".rda"))
write.csv(GMTV, file = paste0("../../data/processed/csv/", fileName, ".csv"))
```

### 2023-06-14 analysis/article/paper.tex
improve reproducability

\begin{keyword}
    Public goods \sep Dynamic
games \sep Reproducibility \sep Generalizability \sep Online
Experiment \sep 
    Climate change mitigation
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, enhanced, breakable, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

Today's actions are tomorrow's result. There are many settings in which
current decisions affect future outcomes and with it, future decision
spaces. Opting for environmental friendly policies today not only
reduces carbon dioxide omissions immediately but also helps us to reach
the Paris climate targets tomorrow. Deferring these policies, may not
necessarily prevent us from reaching these targets, but it requires more
effort in the future compared to a path that includes immediate action.
Aiming at certain goals, today's actions (or the omission thereof) not
only affect intermediate outcomes but also the number of paths one can
choose from that lead to that specific goal.

@@

A game designed by Gächter, Mengel, Tsakas \& Vostroknutov \citeyearpar[
hereafter, GMTV]{GMTV2017} as well as Stefan Große (unpublished) shows
that it is fairly simple to add this element of realism. They
incorporated interdependencies into a \emph{dynamic} public goods game
(dPGG) by defining endowments as the income of previous periods. To put
it differently, participants' actions in a given period affect their
number of actions in subsequent periods: the more (less) they earn now,
the more (less) they can contribute in the next period. Importantly,
this modification qualitatively yields the same rational predictions as
the static game (i.e.~free-riding and the under-provision of the public
good). It is thus, equally well suited to study dilemma situations.

@@

\citet{AGM2018} conducted static public goods games in the lab and on
MTurk to draw lessons from online experimentation. This study extends
this literature \citep[see,
e.g.,][]{SnowbergYariv_2021, GuptaRigottiWilson_2021, GoodmanPaolacci2017, AmirEtAl2012}
by focusing on an \emph{inconvenient} sample (i.e.~one that is
completely inexperienced sample that has not been exposed to interactive
experiments before) playing a computationally more complex game. This
required me to design a robust (and thus, more complex) software to
minimize attrition. I collected paradata---which captures screen time
and survey navigation, for instance---to assess the desired fluency and
feasibility of the experiment. This research reports on the robust
design that made the dynamic game feasible.

>>>>

\begin{keyword}
    Public goods \sep Dynamic
games \sep Reproducibility \sep Generalizability \sep Online
Experiment \sep 
    Climate change mitigation
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, enhanced, sharp corners, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable]}{\end{tcolorbox}}\fi

@@

Today's actions are tomorrow's result. There are many settings in which
current decisions affect future outcomes and with it, future decision
spaces. Opting for environmental friendly policies today not only
reduces carbon dioxide omissions immediately but also helps us to reach
the Paris climate targets tomorrow. Deferring these policies, may not
necessarily prevent us from reaching these targets, but it requires more
effort in the future compared to a path that includes immediate action
\citet{HaenselEtAl2022}. Aiming at certain goals, today's actions (or
the omission thereof) not only affect intermediate outcomes but also the
number of paths one can choose from that lead to that specific goal.

@@

A game designed by Gächter, Mengel, Tsakas \& Vostroknutov \citeyearpar[
hereafter, GMTV]{GMTV2017} as well as Stefan Große (unpublished) shows
that it is fairly simple to add this element of realism. They
incorporate interdependencies into a \emph{dynamic} public goods game
(dPGG) by defining endowments as the income of previous periods.
Consequently, participants' actions in a given period affect their
number of actions in subsequent periods: the more (less) they earn now,
the more (less) they can contribute in the next period. Importantly,
this modification qualitatively yields the same rational predictions as
the static game (i.e.~free-riding and the under-provision of the public
good). It is thus, equally well suited to study dilemma situations.

@@

\citet{AGM2018} conducted static public goods games in the lab and on
MTurk to draw (and report) lessons from online experimentation. This
study extends this literature \citep[see,
e.g.,][]{SnowbergYariv_2021, GuptaRigottiWilson_2021, GoodmanPaolacci2017, AmirEtAl2012}
by focusing on an \emph{inconvenient} sample (i.e.~one that is
completely inexperienced sample that has not been exposed to interactive
experiments before) playing a computationally more complex game. This
required me to design a robust (and thus, more complex) software to
minimize attrition. I collected paradata---which captures screen time
and survey navigation, for instance---to assess the desired fluency and
feasibility of the experiment. Like \citet{AGM2018}, this research is of
practical relevance as it reports on the robust design that made the
dynamic game feasible.
